Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-05-17 paper/paper.tex
Tweak Nutils section

\subsubsection{nutils}

The nutils~\cite{nutils} project can be build using \texttt{buildPythonPackage}, one test needs to be disabled, the rest of the testsuite passed without any issues.
While the preCICE distribution ships with nutils v7.0, one tutorial case requires v6.3 because of the usage of a deprecated function.

>>>>

\subsubsection{Nutils}

The Nutils~\cite{nutils} solver can be build using \texttt{buildPythonPackage}. One test needs to be disabled, but the rest of the testsuite passes without issues. There is no dedicated Nutils-preCICE adapter, but preCICE is typically directly called from Nutils application scripts.
